Goal Document: Translating Typing Rules into JastAdd

### 2023-02-03 GoalDocument.tex
Reformat involved parties

\section{Involved parties}
\subsubsection*{Student}
Nicholas Boyd Isacsson\\ \href{mailto:nicholas@isacsson.se}{nicholas@isacsson.se}
\\
\subsubsection*{Supervisor}
Christoph Reichenbach \\ \href{mailto:christoph.reichenbach@cs.lth.se}{christoph.reichenbach@cs.lth.se}

>>>>

\section{Involved parties}
\subsubsection*{Student}
  Nicholas Boyd Isacsson \\
  \href{mailto:nicholas@isacsson.se}{nicholas@isacsson.se}

\subsubsection*{Supervisor}
  Christoph Reichenbach \\
  \href{mailto:christoph.reichenbach@cs.lth.se}{christoph.reichenbach@cs.lth.se}
